---
output:
  md_document:
    variant: markdown_github
html_preview: false
---


```{r echo=FALSE, results="hide", message=FALSE}
library("txtplot")
library("ypages")
```


#  clusterProfiler

`r badge_bioc_release("clusterProfiler", "green")`
`r badge_devel("clusterProfiler", "green")`
[![Bioc](http://www.bioconductor.org/shields/years-in-bioc/clusterProfiler.svg)](https://www.bioconductor.org/packages/devel/bioc/html/clusterProfiler.html#since)
`r badge_bioc_download("clusterProfiler", "total", "blue")`
`r badge_bioc_download("clusterProfiler", "month", "blue")`

[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![codecov](https://codecov.io/gh/GuangchuangYu/clusterProfiler/branch/master/graph/badge.svg)](https://codecov.io/gh/GuangchuangYu/clusterProfiler/)
[![Last-changedate](https://img.shields.io/badge/last%20change-`r gsub('-', '--', Sys.Date())`-green.svg)](https://github.com/GuangchuangYu/clusterProfiler/commits/master)
[![commit](http://www.bioconductor.org/shields/commits/bioc/clusterProfiler.svg)](https://www.bioconductor.org/packages/devel/bioc/html/clusterProfiler.html#svn_source)
[![GitHub forks](https://img.shields.io/github/forks/GuangchuangYu/clusterProfiler.svg)](https://github.com/GuangchuangYu/clusterProfiler/network)
[![GitHub stars](https://img.shields.io/github/stars/GuangchuangYu/clusterProfiler.svg)](https://github.com/GuangchuangYu/clusterProfiler/stargazers)


[![platform](http://www.bioconductor.org/shields/availability/devel/clusterProfiler.svg)](https://www.bioconductor.org/packages/devel/bioc/html/clusterProfiler.html#archives)
[![Build Status](http://www.bioconductor.org/shields/build/devel/bioc/clusterProfiler.svg)](https://bioconductor.org/checkResults/devel/bioc-LATEST/clusterProfiler/)
[![Linux/Mac Travis Build Status](https://img.shields.io/travis/GuangchuangYu/clusterProfiler/master.svg?label=Mac%20OSX%20%26%20Linux)](https://travis-ci.org/GuangchuangYu/clusterProfiler)
[![AppVeyor Build Status](https://img.shields.io/appveyor/ci/Guangchuangyu/clusterProfiler/master.svg?label=Windows)](https://ci.appveyor.com/project/GuangchuangYu/clusterProfiler)
[![install with bioconda](https://img.shields.io/badge/install%20with-bioconda-green.svg?style=flat)](http://bioconda.github.io/recipes/bioconductor-clusterprofiler/README.html)


This package implements methods to analyze and visualize functional profiles of genomic coordinates (supported by [ChIPseeker](http://www.bioconductor.org/packages/ChIPseeker)), gene and gene clusters.

[![Twitter](https://img.shields.io/twitter/url/https/github.com/GuangchuangYu/clusterProfiler.svg?style=social)](https://twitter.com/intent/tweet?hashtags=clusterProfiler&url=http://online.liebertpub.com/doi/abs/10.1089/omi.2011.0118&screen_name=guangchuangyu)

------------------------------------------------------------------------

Please cite the following article when using `clusterProfiler`:

__*Yu G*__, Wang L, Han Y and He Q^\*^. clusterProfiler: an R package for comparing biological themes among gene clusters. OMICS: A Journal of Integrative Biology. 2012, 16(5):284-287.

`r badge_doi("10.1089/omi.2011.0118", "green")`
`r badge_citation("MLfJN-KU85MC", "2349076811020942117", "green")`
`r badge_altmetric("681089", "green")`

------------------------------------------------------------------------

For details, please visit our project website, <https://guangchuangyu.github.io/clusterProfiler>.

+ [Documentation](https://guangchuangyu.github.io/clusterProfiler/documentation/)
+ [Featured Articles](https://guangchuangyu.github.io/clusterProfiler/featuredArticles/)
+ [Feedback](https://guangchuangyu.github.io/clusterProfiler/#feedback)

### Citation

`r badge_citation("MLfJN-KU85MC", "2349076811020942117", "green")`


```{r echo=F, comment=NA}
d <- get_article_cite_history('DO5oG40AAAAJ', 'MLfJN-KU85MC')
txtplot(d$year, d$cites)
```

### Download stats

`r badge_download_bioc("clusterProfiler")`
`r badge_bioc_download("clusterProfiler", "total", "blue")`
`r badge_bioc_download("clusterProfiler", "month", "blue")`

```{r echo=F, comment=NA}
x <- dlstats::bioc_stats("clusterProfiler")
x <- x[-nrow(x), ] # last month data is not complete
txtplot(ggtree::Date2decimal(x$end), x$Nb_of_downloads, width=100, height=25)
```


